# Explanatory Data Analysis

#### This EDA comes as part of the model building process, where its focus are applicants based on the following focus are termed as 'good or 'bad' risks:

-   Job

-   Property

-   Credit History

-   Employment

-   Purpose

-   Age

-   Credit history

-   personal status

-   housing

#### Importing Libraries

```{r}
library(dplyr) #data manipulation & wrangling
library(moments) #statiscal functions
library(ggplot2) # data visaulisation
```

### Risk Filtering

The goal is to filter the different risks and make assessment with them

```{r}
good_risk <- credit_data_recode %>% filter (assessment =='good')

dim(good_risk)
  
```

```{r}
bad_risk <- credit_data_recode %>% filter (assessment =='bad')

dim(bad_risk)
```

#### Job Assessment

```{r}
jb_assess_bad<- table(bad_risk$job)
jb_assess_good<- table(good_risk$job)

print("Good Risks")
print(jb_assess_good)


print("Bad Risks")
print(jb_assess_bad)

```

```{r}
ggplot(credit_data_recode, aes(x="", y= job, fill = job)) + 
  geom_col()+
  coord_polar(theta = 'y') +
  labs(title = "Distribution Of Loan Applicant Jobs") +
  theme_void() +
  theme(legend.position = 'bottom')
  
```
